\begin{abstract}
Biomedical engineering students must connect circuit diagrams, instrumentation concepts, signals, and feedback systems to executable engineering behavior. General LLM tutors can provide useful explanations, but they are not engineering simulators and do not inherently produce stable MATLAB/Simscape evidence. We present CiTT, a MATLAB-native agentic tutor that grounds circuit tutoring in executable Simulink and Simscape artifacts. CiTT parses circuit images or prompts into structured specifications, prepares SATK/MCP-compatible model-building tasks, opens Simscape/Simulink models, and supports Socratic teaching through focus maps, model highlights, natural-language probes, and evidence export. We evaluate CiTT on three biomedical circuit-learning benchmarks: a textbook RC anti-aliasing filter, a two-electrode voltage clamp equilibrium circuit, and an educational mixed-signal neural-clamp benchmark. The live evidence package shows that CiTT produces inspectable models, screenshots, focus/probe maps, teaching evidence, simulation plots, and explicit limitations. A Gemini-only no-tools baseline performs well on simple RC arithmetic but lacks executable artifacts; on more complex tasks it provides plausible reasoning while requiring simulation or showing ambiguity. CiTT is positioned as educational design-assistance software, not patient-facing software. This draft is a CVPR-style systems paper for course/design-competition review, not a real CVPR submission.
\end{abstract}
